%*******************************************************
% Abstract in English
%*******************************************************
\pdfbookmark[0]{Abstract}{Abstract}


\begin{otherlanguage}{american}
	\chapter*{Abstract}

	\begin{sloppypar}
	\noindent \acs{APT} scanners must be able to analyze compromised or suspicious systems as quickly as possible. In day-to-day use outside incident-response scenarios, they should combine short scan times with low resource utilization.

	\vspace{7.56mm}

	\noindent This thesis investigates performance optimization of an \acs{APT} scanner by replacing object-based, recursively synchronous scheduling with a centralized task-based scheduling model.

	\vspace{7.56mm}

	\noindent Three scheduling algorithms were implemented and evaluated: First-In, First-Out (\acs{FIFO}), Shortest-Subtree-Time-First (\acs{SSTF}), and Work-Stealing with \acs{SSTF} prioritization. The evaluation was conducted experimentally in a controlled test environment on Debian~13 and Windows~11 with one, four, and ten threads and 20 repetitions per configuration. The measured metrics were runtime, \acs{CPU} and \acs{RAM} utilization, waiting time, burst time, and the share of synchronously executed tasks.

	\vspace{7.56mm}

	\noindent On Windows, the new schedulers show clear runtime improvements compared with the reference at four and ten threads, ranging from about 5.69\,\% to 8.39\,\% at four threads and from about 8.89\,\% to 10.38\,\% at ten threads, depending on the method. Under Linux, no consistent runtime advantage can be demonstrated. \acs{SSTF} provides the most stable overall balance of runtime, waiting time, and memory behavior.

	\vspace{7.56mm}

	\noindent The results show that the architectural change is feasible and enables reproducible performance gains, especially in scenarios under heavy system load.
	\end{sloppypar}

\end{otherlanguage}
